E Coli project paper

### 2013-07-15 paper/paper.tex
small changes to paper

The star shape (randst-96) Shows oscillations in nflD horizontally, two poles to two
poles.  There is sometimes a small amount of lag between the upper
maxima moving horizontally and the lower.  Half periods take roughly
25s. Dimensions are roughly 5.00 by 5.00?  Check this.

Randst (sort of triangle) is roughly dimensions of 3.5 by 3.5?
nflD oscillations appear to be half periods of 25s as well.  Maxima appear
at the poles and in the interim there are weak maxima in center pole.

@@

>>>>

The star shape (randst-96) Shows oscillations in nflD horizontally,
two poles to two poles.  There is sometimes a small amount of lag
between the upper maxima moving horizontally and the lower.  Half
periods take roughly 25s. Dimensions are roughly 5.00 by 5.00?  Check
this.  The nflE short bursts do develop lag between when the top and
the bottom go off.  Should coordinate this with the nflD lag.

Randst 97 nflE starts with small maxima, not much difference at all,
then actually builds to high maxima at the poles.

Randst 99 (sort of triangle) is roughly dimensions of 3.5 by 3.5?
nflD oscillations appear to be half periods of 25s as well.  Maxima appear
at the poles and in the interim there are weak maxima in center pole.

@@

Randst nflD doesn't show much oscillation at all, but we start it so
that the density is not max at the pole.
